---
title: "Assignment_4"
author: "Tongxiang Lu"
date: "2022-11-06"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#a.
# Read mydata.
```{r}
mydata <- read.csv("Pharmaceuticals.csv")
mydata
```

# a. Set 3 to 11 as numerical variables (1 to 9) and normalize data.
```{r}
library(tidyverse)
mydata1 <- scale(mydata[, 3:11])
mydata1
```

# Trying to find the optimal k.
```{r}
library(factoextra)
wss <- fviz_nbclust(mydata1,kmeans,method="wss",k.max=20)
wss
```
# I find the optimal K=2 by using the wss method.

```{r}
silhouete <- fviz_nbclust(mydata1,kmeans,method="silhouette",k.max=20)
silhouete
```
# I find the optimal K=5 with the silhouete method.


# Running the kmeans k=2.
```{r}
cluster.kmean <- kmeans(mydata1,centers=2,nstart=2)
cluster.kmean
```

# Data Transformation
```{r}
mydata2 <- cbind(mydata,cluster.kmean$cluster)
colnames(mydata2) <- c("Symbol","Name","Market_Cap","Beta","PE_Ratio","ROE", 
                       "ROA", "Asset_Turnover","Leverage", "Rev_Growth",          
                       "Net_Profit_Margin", "Median_Recommendation","Location",
                       "Exchange", "Groups")
mydata2$Groups <- as.factor(mydata2$Groups)
```

# Getting a condensed value for each of the attribute in each cluster.
```{r}
fit <- kmeans(mydata1, 2)
aggregate(mydata1,by=list(fit$cluster),FUN=mean)
Cluster_Number<- data.frame(mydata1, fit$cluster)
Cluster_Number
```

# I only find two clusters 1 & 2. 
 
 
# Running the kmeans k=5.
```{r}
cluster.kmean <- kmeans(mydata1,centers=5,nstart=2)
cluster.kmean
```

# Data Transformation
```{r}
mydata2 <- cbind(mydata,cluster.kmean$cluster)
colnames(mydata2) <- c("Symbol","Name","Market_Cap","Beta","PE_Ratio","ROE", 
                       "ROA", "Asset_Turnover","Leverage", "Rev_Growth",          
                       "Net_Profit_Margin", "Median_Recommendation","Location",
                       "Exchange", "Groups")
mydata2$Groups <- as.factor(mydata2$Groups)
```

# Getting a condensed value for each of the attribute in each cluster.
```{r}
fit <- kmeans(mydata1, 5)
aggregate(mydata1,by=list(fit$cluster),FUN=mean)
Cluster_Number<- data.frame(mydata1, fit$cluster)
Cluster_Number
```


# b. 
Cluster 1             2, 3, 5, 18, 20
It has the highest Market capitalization, ROE, ROA, Asset Turnover and
lowest leverage.
Cluster 2             1, 4, 7, 10, 16, 19
It has the least Beta(risk), high ROE, high ROA, good revenue growth and 
high Net Profit Margin.
Cluster 3             6, 8, 9, 12, 14
It  has a low market cap, high Beta(risk), lowest asset turnover, good profit 
and highest revenue growth.
Cluster 4             11, 13, 15, 17
It has the highest Beta, low market cap, low ROE, low ROA, least revenue growth and least net profit margin.
Cluster 5             21
It has the highest market cap with high Asset turnover, low Beta(risk) and 
a greater profit margin.


# c.
Cluster 1- It indicates "advised best-buy" pattern, based on its highest Market capitalization, ROE, ROA, Asset Turnover, and lowest leverage.
Cluster 2- It indicates "hold or buy" pattern, due to highest Price earning ratio, strong asset turnover ratio with lowest or negative beta.
Cluster 3- It shows "hold" recommendation because of strong Assets turnover 
ratio, and the company could use their assets efficiently to generate the 
revenue with highest net profit margin and lowest leverage.
Cluster 4 It has no pattern.
Cluster 5 It has no pattern.


# d. 
Cluster 1 can be named as ' Advised best-buy investment', because it has an 
average asset turnover and average revenue growth. With highest PE Ratio among
all the clusters.  
Cluster2 can be named as 'Advised stable investment' as it has the least 
Beta(risk), high ROE, high ROA, good revenue growth and high Net Profit Margin.
Cluster 3 can be named as 'Advised less investment'，as it has a low market cap, high Beta(risk), lowest asset turnover, good profit and highest revenue growth.
Cluster 4 can be named as 'Advised least investment', for it has the highest 
Beta, low market cap, low ROE, low ROA, least revenue growth and least net 
profit margin.
Cluster 5 can be named as 'Advised safest investment'，as it has the highest 
market cap with high Asset turnover, low Beta(risk) and a profit margin greater than all other clusters. 










