---
title: "ML Final Exam"
author: "Tongxiang Lu"
date: "2022-12-12"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load the data.
```{r}
fuel_costs.df <- read.csv("fuel_receipts_costs_eia923.csv")
```

# Set random four digit seed and split data.
```{r}
library(caret)
set.seed(3272)
fuel_costs.df1<-createDataPartition(fuel_costs.df$fuel_type_code_pudl,p=0.02,list=F)
Sampled_Data = fuel_costs.df[fuel_costs.df1,]

Train_Index=createDataPartition(Sampled_Data$fuel_type_code_pudl, p=0.75, list=F)
Train_Data=Sampled_Data[Train_Index,]
Validation_Data=Sampled_Data[-Train_Index,]
```

# Remove the missing value.
```{r}
library(dplyr)
sapply(Train_Data,function(x) sum(is.na(x)))
head(Train_Data)
```
# Set only numerical variable for my train data analysis.
```{r}
fuel_costs.df1 <- Train_Data[c(2,15,16,17,18,20)]
head(fuel_costs.df1)
summary(fuel_costs.df1)
```
# Drop column 6 as it has significant number of missing data.
```{r}
fuel_costs.df2 <- fuel_costs.df1[,-6]
summary(fuel_costs.df2)
```
# Set only numerical variable for my test data analysis.
```{r}
fuel_costs.df1_valid <- Validation_Data[c(2,15,16,17,18,20)]
summary(fuel_costs.df1_valid)
```
# Drop column 6 as it has significant number of missing data.
```{r}
fuel_costs.df2_valid <- fuel_costs.df1_valid[,-6]
summary(fuel_costs.df2_valid)
```
# Normalize data.
```{r}
library(tidyverse)
fuel_costs.df3 <- scale(fuel_costs.df2[,1:5])
head(fuel_costs.df3)
fuel_costs.df3_valid<-scale(fuel_costs.df2_valid[,1:5])
head(fuel_costs.df3_valid)
```
# Trying to find the optimal k
```{r}
library(factoextra)
wss <- fviz_nbclust(fuel_costs.df3,kmeans,method="wss")
wss
# It is very ambiguous to find the optimal K.
```

```{r}
silhouete <- fviz_nbclust(fuel_costs.df3,kmeans,method="silhouette")
silhouete
# I find my optimal K=7 by silhouete method.
```
# By WSS and silhouette method comparasion, I find silouette method more precise, 
so I choose running kmeans k=7.
```{r}
cluster.kmean <- kmeans(fuel_costs.df3,centers=7,nstart=25)
cluster.k1<-kmeans(fuel_costs.df3,centers = 7, nstart = 25)
fviz_cluster(cluster.k1, data = fuel_costs.df3)
cluster.k1$size
cluster.k1$centers
```

# Interpretation
Cluster 1
This cluster receives a very high volume of fuel（big positive numbers) with 
low ash and sulfur(negative numbers), which means this cluster accumulated pure 
fuel. Thus, I conclude this cluster with surplus inflow of pure fuel. Additionally, 
the positive number of plant indicates that the plant with larger identification 
number is relevant to the large volume of fuel.

Cluster 2
This cluster is identified as everything low with low quantity of fuel received, 
low heat content of the fuel, low sulfur content percentage and low ash content 
as well. Both the negative and positive things are low here.

Cluster 3
This cluster is basically characterized with the highest ash content in the fuel, 
in which the most impure energy is located with high heat content of the fuel, 
high sulfur content and high ash content percentage. So, I recommend US power 
generation to bring proper policy to curb the impurity in the fuel.

Cluster 4
This is the highest fuel received cluster with low ash content. Such a large 
volume of relatively purer fuel! Contrary to cluster 3, US power generation can 
use the incentive policy to further encourage collecting good fuel with less ash content.

Cluster 5
Cluster 5 has higher heat value of the fuel together with moderately high 
sulfur content and ash content. My conclusion is cluster 5 has more fuel 
with more efficiency and releases more energy.

Cluster 6
This is the cluster with everything low. The difference between cluster 2 and 
cluster 6 is that this cluster has the plant with smaller identification numbers 
than cluster 2.  Contrary to cluster 1, this cluster shows that the plants 
with lower identification number are associated with low volume of fuel.

Cluster 7
Cluster 7 can be named as a larger volume of fuel than average with very 
high sulfur content in it. From the perspective of emission control and the 
longevity of automobiles, this is the cluster the US power generation must keep 
an eye on and formulate policy to reduce the sulfur content. 





