---
title: "Regression assignment"
author: "Tongxiang Lu"
date: "2022-11-10"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Question 1
```{r}
set.seed(2017)
X=runif(100)*10
Y=X*4+3.45
Y=rnorm(100)*0.29*Y+Y
plot(X,Y)
```
 
## Question 1a     
Based on the plot, I think it fits a linear model because the graph shows 
positive relationship between X and Y, when Y increases, X increases.


```{r}
Model =lm(Y~X)
Model
summary(Model)
```
## Question 1b
The regression equation is Y=4.465 + 3.611*X. 
From summary, I get R2 0.65 which means the model explains 65% variability of Y variable, however, we still miss 35% variability, thus X is just a not-bad 
predictor of Y.


```{r}
cor(X,Y)^2
```
## Question 1c
From summary, I get R2 65%, and I get correlation coefficient of X and Y is 65%, therefore, they are greatly related to each other.

# Question 2
```{r}
head(mtcars)
lm(formula = mtcars$hp ~ mtcars$wt, data = mtcars)
lm(formula = mtcars$hp ~ mtcars$mpg, data = mtcars)
```
## Question 2a
Based on the above data, I think James is right for his correlation coefficient 
(hp and weight)is 46.160, which is much bigger than Chris's correlation 
coefficient(hp and mlp) which is -8.83. Thus, weight is more related to HP than 
mlp.

```{r}
Model=lm(mtcars$hp ~ mtcars$cyl + mtcars$mpg, data = mtcars)
Model
HP=54.067+ 23.979*4 - 2.775*22
HP
```
## Question 2b
The estimated Horse Power of a car with 4 calendar and mpg of 22 is 88.933.

# Question 3
```{r}
library(mlbench)
data(BostonHousing)
Model=lm(BostonHousing$medv~BostonHousing$crim + (BostonHousing$zn > 25) +  
         BostonHousing$ptratio+BostonHousing$chas)
summary(Model)
```
## Question 3a
From summary, I get R2 34%, while we miss 66% data, my conclusion is that this 
is not an accurate model.
   

## Set Model1 as houses bounds the Chas River, Model 2 as houses bounds no river.
```{r}
Model1=lm(BostonHousing$medv~BostonHousing$crim + (BostonHousing$zn > 25) +  
         BostonHousing$ptratio+BostonHousing$chas)
Model1
Model2=lm(BostonHousing$medv~BostonHousing$crim + (BostonHousing$zn > 25) +  
         BostonHousing$ptratio)
Model2
```
## Question 3b
From the data shown, the house bounds the river is more expensive than the house
bounds no river, by US$4292.1 per square. 

## Question 3c
## I get smallest p-value < 2.2e-16 with BostonHousing$ptratio variable, that is,  pupil-teacher ratio by town has a biggest influence to Boston housring compared 
with the other three variables such as crime(per capita crime rate by town),
chas(Charles River) and zn(proportion of residential land zoned for lots 
over 25,000 sq.ft).


## Question 3d
```{r}
anova(Model)
```
## From anova analysis, we learn the sum sq of crim, zn, ptratio are all big 
values whereas the chas is small value, in other words, crim has the first 
important influence to Bostonhousing price, ptratio the second, zn the 
third, whereas chas has the least influence to Bostonhousing price. 
